
\documentstyle[11pt]{article}
\textheight 9.0in
\textwidth 6.5in
\oddsidemargin 0.0in
\topmargin -0.5in
\setlength{\floatsep}{0.3cm}
\setlength{\textfloatsep}{0.3cm}
\setlength{\intextsep}{0.3cm}
\newcommand{\definedas} {\stackrel{\Delta} {=}}
% Include the macros for including postscript figures in latex - CSG
\input{./psfig}


%\parindent 0pt
\begin{document}
% \setlength{\parindent}{5pt}
% \setlength{\parskip}{0.25cm}
\bibliographystyle{unsrt}

\include{cover_title}

\include{cover_abstract}

\section{Comments}
The following section contains a description of how the
{\em k--way.x} \cite{Kuznar93a} partitioning algorithm was interfaced to
the Xilinx tool, XACT. Other partitioning algorithms may be interfaced with
the Xilinx Design Development System in a similar manner. This document is
intended to provide users of the Partitioning benchmark suite with guidelines
about interfacing their partitioning algorithms to the Xilinx Design
Development System. 

\section{Software Implementation of the k--way Partitioning Algorithm}

We implemented the proposed k--way partitioning algorithm in the C 
language and designed interfaces to the Xilinx tool XACT \cite{Xil91a}.
In Figure \ref{k-way.interface} we illustrate the process of using our 
partitioning tool, {\sl k--way.x}, as an extension of the XACT Design 
Development System.

\subsection{Interface to the XACT Xilinx Development System}

\input{./figure}

The input data to {\sl k--way.x} is a design description given in the 
$XNF$ format as a netlist of gate primitives.
Using the XACT software, this description can be readily mapped into a 
netlist of CLBs and IOBs represented in the $MAP$ format.
The need for partitioning arises when the mapped netlist does not fit 
into any FPGA package available in the device library.
Furthermore, partitioning can be used to minimize the design cost, even 
if it is possible to implement the design as a single, large FPGA IC.
For example, it is possible that the smallest FPGA chip with a 
sufficient number of CLBs is unroutable, forcing the designer to use
a larger device, capable of not only containing all CLBs but also 
yielding a 100\% routing completion.
This larger device may be significantly oversized compared to the 
design size; in other words, its CLB utilization may be very poor.
If the design is partitioned, it is possible that a number of smaller 
devices with higher CLB utilization could be used, thus reducing the 
design cost.
\par
Currently, the designer has to perform the partitioning manually.
In certain cases this task may be manageable, e.g., if the circuit 
was designed by a designer using schematic capture tools.
However, the partitioning task may be exceedingly difficult when its 
subject is a large netlist, e.g., generated automatically by a 
high--level synthesis tool.
An automatic partitioning tool is the only practical alternative in the 
latter case.

\bibliography{fpga}

\end{document}
